Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2020-05-23 doc/network.tex
one more

The likelihood of the non-homogeneous Poisson process can be written as:
\begin{equation}\label{eq:nonhomogeneous}
\begin{aligned}
&\mathcal{L}(\Lambda, \theta\,|\, \mathbf{s}, \mathbf{t}, \mathbf{n}, \tsub{t}{truncate})\\
&\quad=\prod_{j=1}^N \left(\Lambda^{n_j} \exp \big(- \Lambda \, F_0(\tsub{t}{truncate} - t_j ;\theta) \big) \prod_{i=1}^{n_j} f_0(s_{i, j}; \theta) \right),
\end{aligned}
\end{equation}
where $N$ is the total number of infected individuals.
Here, we estimate parameters $\Lambda$ and $\theta$ by maximum likelihood.
We then use the estimated distribution $f_0$ to infer the initial reproductive number $\Rini$ from the estimated growth rate (using the Euler-Lotka equation).
We expect estimates of $\Lambda$ to be sensitive to under-reporting.
White and Pagano \cite{forsberg2008likelihood} proposed a related approach based on discretized incidence reports.

>>>>

The likelihood of the non-homogeneous Poisson process can be written as:
\begin{equation}\label{eq:nonhomogeneous}
\begin{aligned}
&\mathcal{L}(\Lambda, \theta\,|\, \mathbf{s}, \mathbf{t}, \mathbf{n}, \tsub{t}{truncate})\\
&\quad=\prod_{j=1}^N \left(\Lambda^{n_j} \exp \big(- \Lambda \, F_0(\tsub{t}{truncate} - t_j ;\theta) \big) \prod_{i=1}^{n_j} f_0(s_{i, j}; \theta) \right),
\end{aligned}
\end{equation}
where $N$ is the total number of infected individuals.
Here, we estimate parameters $\Lambda$ and $\theta$ by maximum likelihood.
We then use the estimated distribution $f_0$ to infer the initial reproductive number $\Rini$ from the estimated growth rate (using the Euler-Lotka equation).
When the entire transmission process is known, we expect $\Lambda$ to match $\Rini$;
otherwise, $\Lambda$ will be sensitive to under-reporting of number of infections caused by each infected individual.
As we show in Appendix A.3, the estimates of $\Rini$ using the Euler-Lotka equation from $f_0$ remains unbiased even in the presence of under-reporting.
White and Pagano \cite{forsberg2008likelihood} proposed a related approach based on discretized incidence reports.
